Untargeted control doc

### 2023-09-30 untargeted/paruntargeted_control.Rmd
Adding factors to parametadata on first read in

parametadata <- read_csv("metadata/parametadata.csv") %>% 
  filter(polarity==!!polarity) %>%
  filter(amendment==!!amendment) %>%
  filter(IS_type==!!IS_type)

>>>>

parametadata <- read_csv("metadata/parametadata.csv") %>% 
  filter(polarity==!!polarity) %>%
  filter(amendment==!!amendment) %>%
  filter(IS_type==!!IS_type) %>%
  mutate(startime=factor(startime, levels=c("Morn", "Eve"))) %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(timepoint=factor(timepoint, levels=paste0("T", c(0,1,3,10,26,73))))
